Discovery of the first quadruple gravitationally lensed quasar candidate with Pan-STARRS

### 2017-06-14 manuscript.tex
minor change

These applications all require increasingly large samples of lensed quasars, and in particular quadruply lensed quasars (quads), due to the increased number of modeling constraints they provide. To date, there are only about three dozen known quads over the whole sky\footnote{http://masterlens.astro.utah.edu/}. Due to the rare nature of lensed quasars, large scale surveys of sufficient depth and resolution are required to significantly increase the present sample \citep{ogu10}. As such surveys have become available, pioneering searches for lensed quasars, such as the Cosmic Lens All Sky Survey \citep[CLASS;][]{mye03} have been succeeded by the SDSS Quasar Lens Search \citep[SQLS;][]{ogu06}, and more recently by the STRong lensing Insight in the Dark Energy Survey \citep[STRIDES;][]{agn15} and the Survey of Gravitationally-lensed Objects in HSC Imaging \citep[SuGOHI;][]{son17}, amongst others.

>>>>

These applications all require increasingly large samples of lensed quasars, and in particular quadruply lensed quasars (quads), due to the increased number of modeling constraints they provide. To date, there are only about three dozen known quads over the whole sky\footnote{http://masterlens.astro.utah.edu/}. Due to the rare nature of lensed quasars, large scale surveys of sufficient depth and resolution are required to significantly increase the present sample \citep{ogu10}. As such surveys have become available, pioneering searches for lensed quasars, such as the Cosmic Lens All Sky Survey \citep[CLASS;][]{mye03} have been succeeded by the SDSS Quasar Lens Search \citep[SQLS;][]{ogu06}, and more recently by the STRong lensing Insight in the Dark Energy Survey \citep[STRIDES;][]{agn15} and the extension to SQLS using the Baryon Oscillation Spectroscopic Survey \citep[BQLS;][]{more16}, amongst others.
